Estimation of cloud-corrected microwave humidity radiances with associated uncertainties

### 2020-11-09 Article/ici_submm_cloudcorr.tex
merged table 5 and 6, addded Simon's suggestions

We are here approaching cloud filtering task from a new angle. The basic idea
is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
(i.e.\ the radiance that would have been measured in absence of noise and
hydrometeors). This is done for each channel separately, only using
measurements (no ``background'' data involved). Not only a best estimate is
provided, but also a case specific uncertainty. This information can be used as a pure filter, by rejecting data where the correction exceeds some threshold value. This threshold value should be
relatively low, to not introduce a bias in filtered dataset. However, even
better is to replace the original value with the predicted NFCS value when
forming the clear-sky dataset. We denote this approach as cloud correction. It
is shown below that a basically bias free cloud correction can be obtained.
This feature removes the need of threshold value, as long as the retrieval or
assimilation system can incorporate the uncertainty of the corrected value. As
also will be shown, the uncertainty for originally clear sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach allows that the full weight of
clear-sky data can be preserved.

@@

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}). CloudSat\citep{Stephens2002cloudsat} profiles during August 2015 are randomly selected for forward simulations. The input data are restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are simulated, respectively. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

@@

As has been shown in \citet{pfreundschuh:aneur:18}, QRNN can be used to solve these type of problems. Instead of a point prediction, as it is typically performed in regression problems, QRNNs learn to
predict a vector of quantiles, which can be used to approximate the distribution
of the predicted quantity conditional on the network inputs. Using QRNNs to
perform probabilistic cloud correction thus not only allows deriving an estimate
for $\ynfcs$ but also for the error of the corrected observations.

For this application, the predicted percentiles are chosen to be
$0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
distribution with mean $\mu$ and standard deviation $\sigma$, the quantiles
approximately correspond to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
, \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
estimation of the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.

QRNN's are trained to minimize the mean of the quantile loss functions
%
\begin{align}
  \mathcal{L}_\tau(y_\tau, y) &=
  \begin{cases}
    \tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
    \\
  \end{cases}
\end{align}
%
for all predicted quantile fractions $\tau$, where $\y_\tau$ is the predicted
quantile and $y$ the reference value from the training set. The quantile loss is
used in this study as a performance criterion for the tuning of the hyper
parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In addition to the quantile loss, also the Continuously
Ranked Probability Score (CRPS) is considered. Given a predicted cumulative
distribution function (CDF) $F$ and the reference value $y$, the CRPS is defined as
%
\begin{align}
  \text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
\end{align}
%
To compute the CRPS for a predictions from a QRNN, the predicted quantiles are
used to derive a piece-wise linear approximation of the CDF of the predicted
distribution and evaluate the above integral.

The implementation of QRNN is similar to one described in \citet{pfreundschuh:aneur:18}, except that instead of Keras python package, PyTorch, an open source machine learning
library \citep{paszke2017automatic} is used. This version is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}]. The major challenge for implementing QRNN for the current application was to select high performing neural network architecture. This was obtained through grid search over different hyper-parameter configurations. The details are described in Appendix~\ref{appendix:hyperparamter}

\subsubsection{QRNN model configurations}
%
\label{sec:QRNN_configuration}
In the study, two QRNN configurations are formulated for cloud-correction. The basic construction of both is to individually train for each of the available 183\,GHz channels, using certain input training data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The output in both configurations is the posterior distribution of NFCS values for the target 183\,GHz channel. The two configurations differ only by the number of input 183\,GHz channels used in the training process:

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values described over the chosen quantiles. In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the predicted quantiles for three different cases. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most analysis, usually a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

For probabilistic predictions, accuracy of the point estimate is inadequate to gauge the complete performance. In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also the correct underlying uncertainty. An ideal QRNN output should be sharp or in other words, all predicted quantiles should be concentrated in the vicinity of the point estimate. The predicted posterior distribution should also be well calibrated, that is, reflect the a priori probability distribution. A straightforward way to compare the two distributions is to plot the frequency of predictions and frequency of the true value in different prediction intervals. This is also commonly known as calibration plot. In a well-calibrated QRNN model, the calibration plot should follow the straight line y = x. Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare the predicted and observed errors. The predicted error is deviation of a random sample drawn from the posterior distribution to its median. In this study, we analyse both the calibration plot and the predicted errors to assess the correctness of predicted uncertainties.

All evaluation results described in the study have been made on the test dataset.

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
	\caption{Distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/MWHS_error_dist_14.pdf} 
	\caption{Error distribution for deviations of point estimates to NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates, while ``Predicted(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded.}
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{Error statistics for deviations of point estimates to NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. }
	\label{tab:error_statistics_mwhs_14}
	\begin{tabular}{lrr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c}{QRNN-all}\\
		\cline{2-11}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c}{89+150+183\,GHz}\\		
		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)\\
		\middlehline
		Bias      &  0.00 &  -0.84 & -0.09 & -0.08(3.3\%) & -0.04 & -0.03(3.4\%) & -0.09 & -0.09(3.2\%) & -0.09(3.3\%) & -0.08(3.3\%)  \\
		MAE       &  0.80 &   1.45 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59\\
		STD       &  1.00 &   3.90 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83\\
		skewness & -0.00 & -14.34 & -1.11 & -0.93 & -1.00 & -0.84 & -0.88 & -0.98 & -1.58 & -1.62\\
		\bottomhline
	\end{tabular}
\end{table*}

The posterior distribution of NFCS values obtained from experiment 89+150\,GHz is similar to one shown in Fig.~\ref{fig:posterior_distribution_I1V}. The median value is chosen as the point estimate (see Sect.~\ref{sec:validation}). The distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently. The deviations of point estimates from NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large negative deviations are corrected successfully with QRNN, but residual cloud impact is evident in the negative tail. Most of these residual cases have departures less than 10\,K. The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected data, the negative departures due to cloud impact lead to a large negative skewness(-14.34) and high bias (-0.84\,K). Training QRNN with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.09\,K. However, high skewness values indicate a negative tail or uncorrected departures. Including 118\,GHz in the training, gives comparable results as 89+150\,GHz. With 118\,GHz, the error distributions have lower bias and are more symmetric, but the MAE and STD remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz. In the latter, predictions have the most symmetric error distributions, but the highest spread.

Further we investigated that if filtering the predictions with low accuracy could help in improving the error distributions. For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations. In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed. With 5\,K threshold though the cases with high errors are removed, the persistent negative skewness indicates presence of cases with residual cloud impact. Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases. Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy. For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\% of data, but the negative skewness is still not completely removed.

In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}. SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases. They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ and $183.31\pm 1.00$ as a measure of cloud impact. Further in the text we refer this filter as ``B183''. The results obtained with SI and B183 are displayed in Table~\ref{tab:SI_statistics}. With SI threshold = 5\,K, almost 30\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN. The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear. Similar is the case with B183. Here only 3\% of the data is filtered out but the overall statistics are worse than both QRNN and SI. The results from the two filters are not surprising as both aim at removing only cases with high ice content. The thin cirrus clouds and other low hydrometeor impact cases remain unaltered.

@@

\subsubsection{QRNN-single applied to channel 11, 12, 13 and 15}
\label{sec:mwhs_others}
\begin{table*}[t]
	\caption{ Error statisics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz. The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}.}
	\label{tab:error_statistics_mwhs_others}
	\begin{tabular}{lrrr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
		\cline{2-6}
		%		\hline
		& &  Clear-sky &   All-sky &  \multicolumn{2}{c}{89+150\,GHz}  \\
		&	&		   &			& All & Pred.(5K)\\
		\middlehline
		Channel 11  &   Bias      & 0.00 &  -0.16 & -0.03 & -0.03(0.2\%)  \\
				    &	MAE       & 0.80 &   0.89 &  0.79 &  0.79  \\
					&	STD       & 1.00 &   1.71 &  1.03 &  1.01  \\
					&	skewness & 0.01 & -20.18 & -0.68 & -0.45  \\
		\middlehline
		Channel 12  & Bias      & -0.00 &  -0.28 & -0.05 & -0.05(0.6\%)  \\
					& MAE       &  0.80 &   0.98 &  0.81 &  0.80  \\
					& STD       &  1.00 &   2.26 &  1.07 &  1.05  \\
					& skewness &  0.00 & -20.72 & -0.91 & -0.70  \\
		\middlehline
		Channel 13  & Bias      & -0.00 &  -0.52 & -0.08 & -0.07(1.6\%)  \\
					& MAE       &  0.80 &   1.17 &  0.84 &  0.83  \\
					& STD       &  1.00 &   3.04 &  1.13 &  1.10  \\
					& skewness &  0.02 & -17.85 & -1.14 & -0.98 \\		
		\middlehline
		Channel 15  & Bias      & -0.00 &  -1.28 & -0.07 & -0.06(5.6\%)  \\
					& MAE       &  0.80 &   1.87 &  0.97 &  0.92 \\
					& STD       &  1.00 &   5.08 &  1.35 &  1.25 \\
					& skewness & -0.00 & -11.15 & -0.60 & -0.83  \\ 
		\bottomhline
	\end{tabular}
\end{table*}
\begin{table*}[t]
	\caption{Channel wise error statistics obtained after filtering MWHS-2 humidity observations  according to scattering index (SI) and filtering described by \citet{buehler:aclou:07}. The latter is denoted as  B183. }
	\label{tab:SI_statistics}
	\begin{tabular}{lrr|rr|rr|rr|rr}
		\tophline
		& \multicolumn{2}{c|}{Channel 11} & \multicolumn{2}{c|}{Channel 12} & \multicolumn{2}{c|}{Channel 13} & \multicolumn{2}{c|}{Channel 14} & \multicolumn{2}{c}{Channel 15}\\
			& SI & B183 & SI & B183 & SI & B183 & SI & B183 & SI & B183\\
			\cline{2-11}
		Bias 	 &-0.04	& -0.05	& -0.07 &  -0.15 &  -0.14 & -0.29	&-0.23 &  -0.51 & -0.33 &  -0.81\\
		MAE  	 & 0.81	&  0.81	&  0.82 &	0.86 &	 0.85 &  0.97   & 0.92 &   1.14 &  1.03 &	1.44\\
		STD  	 &1.02	&  1.03	&  1.04 &	1.14 &	 1.1  &  1.39	& 1.26 &   1.83 &  1.53 &	2.64\\
		Skewness &-0.12 & -0.24 & -0.38 & -0.86  &  -0.91 & -2.23   &-1.79 &  -3.45 & -2.85 &  -4.41\\
		\bottomhline		
	\end{tabular}
\end{table*}

>>>>

We are here approaching cloud filtering task from a new angle. The basic idea
is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
(i.e.\ the radiance that would have been measured in absence of noise and
hydrometeors). This is done for each channel separately, only using
measurements (no ``background'' data involved). Not only a best estimate is
provided, but also a case specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even
better is to replace the original value with the predicted NFCS value when
forming the clear-sky dataset. We denote this approach as cloud correction. It
is shown below that a basically bias free cloud correction can be obtained.
This feature also removes the need of threshold value, as long as the retrieval or
assimilation system can incorporate the uncertainty of the corrected value. As
also will be shown, the uncertainty for originally clear sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach allows that the full weight of
clear-sky data can be preserved.

@@

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}). CloudSat\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for forward simulations. The input data are restricted between $60\unit{^{\degree}S}$ to
$60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are simulated, respectively. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

@@

As has been shown in \citet{pfreundschuh:aneur:18}, QRNNs can be used to solve
these type of problems. Instead of a point prediction, the QRNN is trained to
predict a vector of quantiles of the distribution of the target variable
conditional on the network input. Using these predicted quantiles, the cumulative
distribution function (CDF) of the target variable can be estimated. QRNNs thus
not only allow to predict a value $\ynfcs$ for the corrected brightness temperatures
but also to estimate the uncertainty of the correction.

For this application, the predicted percentiles are chosen to be
$0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
distribution with mean $\mu$ and standard deviation $\sigma$, these quantiles
approximately correspond to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
, \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
estimation of the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.

QRNN's are trained to minimize the mean of the sum of the quantile loss functions
%
\begin{align}
\mathcal{L}_\tau(y_\tau, y) &=
\begin{cases}
\tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
\\
\end{cases}
\end{align}
%
for all selected quantile fractions $\tau$, where $y_\tau$ is the predicted
quantile and $y$ the reference value from the training or test data . The
quantile loss is used in this study as a performance criterion for the tuning of
the hyper parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In
addition to the quantile loss, also the Continuously Ranked Probability Score
(CRPS) is considered. Given a predicted CDF
$F$ and the reference value $y$, the CRPS is defined as
%
\begin{align}
\text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
\end{align}
%
To compute the CRPS for a prediction from a QRNN, the predicted quantiles are
used to derive a piece-wise linear approximation of the CDF of the predicted
distribution.

The implementation of QRNN is similar to the one described in
\citet{pfreundschuh:aneur:18}, except that this version uses PyTorch
\citep{paszke2017automatic} instead of Keras \citep{chollet2015keras} to
implement the underlying neural network. The implementation is available as a
part of version of the Typhon software package \citep{typhonv08}. The major
challenge for implementing QRNN for the current application was to select high
performing neural network architecture. This was obtained through grid search
over different hyper-parameter configurations. The details are described in
Appendix~\ref{appendix:hyperparamter}

\subsubsection{QRNN model configurations}
%
\label{sec:QRNN_configuration}
In the study, two QRNN configurations are formulated for cloud-correction. The
basic construction of both is that a separate network is trained for each
183\,GHz channel to correct, using certain input data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The
output in both configurations is the posterior distribution of NFCS values for
the target 183\,GHz channel. The two configurations differ only by the number of
input 183\,GHz channels used in the training process:

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values described over the chosen quantiles. In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the predicted quantiles for three different cases. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most applications only a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we chose the posterior median as the best estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

For probabilistic predictions, accuracy of the point estimate is inadequate to
gauge the complete performance. In a successful QRNN training, QRNN learns to
predict not only an accurate point estimates but also the correct underlying
uncertainty. An ideal QRNN output should be sharp or in other words, all
predicted quantiles should be concentrated in the vicinity of the point
estimate, but at the same time, the predicted posterior distribution should be
well calibrated, that is, the predicted distribution should reflect actually
observed frequencies. A straightforward way to compare the two distributions is
to plot the frequency of predictions and frequency of the true value in
different prediction intervals. This is also commonly known as calibration plot.
In a well-calibrated QRNN model, the calibration plot should follow the straight
line $y = x$. Another way to assess how well the predicted posterior distribution
reflects the observed errors is to compare the predicted and observed errors.
The predicted error is the deviation of a random sample drawn from the posterior
distribution to its median. In this study, we analyse both the calibration plot
and the predicted errors to assess the correctness of predicted uncertainties.

All evaluation results except hyper-parameter tuning, described in the study have been made on the test dataset. Hyper-parameter tuning is made on the training dataset (see Appendix~\ref{appendix:hyperparamter}).

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
	\caption{Distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/MWHS_error_dist_14.pdf} 
	\caption{Error distribution for deviations of point estimates to NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates. The error distribution achieved with scattering index (SI) filtering is also shown. }
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{Error statistics for deviations of point estimates to NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. }
	\label{tab:error_statistics_mwhs_14}
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
		\cline{3-13}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)&&\\
		\middlehline
bias     & -0.00 &  -0.83 & -0.09 & -0.08 & -0.04 & -0.03 & -0.09 & -0.09 & -0.09 & -0.08 & -0.24 & -0.51\\
mae      &  0.80 &   1.44 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59 &  0.92 &  1.14\\
std      &  1.00 &   3.89 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83 &  1.26 &  1.83\\
skewness &  0.01 & -14.40 & -1.11 & -0.96 & -1.02 & -0.86 & -0.89 & -1.02 & -1.61 & -1.58 & -1.79 & -3.45\\
rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.1\%& 3.5\%\\
\bottomhline
	\end{tabular}
\end{table*}

The posterior distribution of NFCS values obtained from experiment 89+150\,GHz is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V}. The median value is chosen as the point estimate (see Sect.~\ref{sec:validation}). The distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently. The deviations of point estimates from NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large negative deviations are corrected successfully with QRNN, but residual cloud impact is evident in the negative tail. Most of these residual cases have departures less than 10\,K. The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected data, the negative departures due to cloud impact lead to a large negative skewness(-14.34) and high bias (-0.84\,K). Training QRNN with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.09\,K. However, high skewness values indicate a negative tail or uncorrected departures. Including 118\,GHz in the training, gives comparable results as 89+150\,GHz. With 118\,GHz, the error distributions have lower bias and are more symmetric, but the MAE and STD remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz. In the latter, predictions have the most symmetric error distributions, but the highest spread.

Further we investigated whether filtering the predictions with low accuracy could help in improving the error distributions. For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations. In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed. With 5\,K threshold though the cases with high errors are removed, the persistent negative skewness indicates presence of cases with residual cloud impact. Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases. Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy. For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\% of data, but the negative skewness is still not completely removed.

In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}. SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases. They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ and $183.31\pm 1.00$ as a measure of cloud impact. Further in the text we refer this filter as ``B183''. The results obtained with SI and B183 are displayed in last two columns of Table~\ref{tab:error_statistics_mwhs_14}. With SI threshold = 5\,K, almost 30\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN. The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear. Similar is the case with B183. Here only 3\% of the data is filtered out but the overall statistics are worse than both QRNN and SI. The results from the two filters are not surprising as both aim at removing only cases with high ice content. The thin cirrus clouds and other low hydrometeor impact cases remain unaltered.

@@

\subsubsection{QRNN-single applied to channel 11, 12, 13 and 15}
\label{sec:mwhs_others}
\begin{table*}[t]
	\caption{ Error statisics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz. The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}. The statistics from existing filtering approaches: scattering index (SI), and scheme by \citet{buehler:aclou:07} are also provided. The latter is denoted as ``B183''.}
	\label{tab:error_statistics_mwhs_others}
	\begin{tabular}{lrrr|rr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c|}{QRNN-single} & \multicolumn{2}{c}{Pure filtering} \\
		\cline{2-8}
		%		\hline
		& &  Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz}    & SI & B183  \\
		&	&		   &			& All & Pred.(5K) &&\\
		\middlehline
		Channel 11  &   Bias      & 0.00 &  -0.16 & -0.03 & -0.03		 &-0.04	& -0.05 \\
				    &	MAE       & 0.80 &   0.89 &  0.79 &  0.79  		 & 0.81	&  0.81 \\
					&	STD       & 1.00 &   1.71 &  1.03 &  1.01 		 & 1.02	&  1.03 \\
					&	skewness  & 0.01 & -20.18 & -0.68 & -0.45 		 &-0.12 & -0.24 \\
					& rejection   & -    & -      & -	  & 0.2\%        & 28.1\% & 3.5\%  \\
		\middlehline
		Channel 12  & Bias      & -0.00 &  -0.28 & -0.05 & -0.05		&  -0.07 & -0.15 \\
					& MAE       &  0.80 &   0.98 &  0.81 &  0.80  		&   0.82 &	0.86 \\
					& STD       &  1.00 &   2.26 &  1.07 &  1.05  		&  1.04  &  1.14 \\
					& skewness  &  0.00 & -20.72 & -0.91 & -0.70  		&  -0.38 & -0.86 \\
					& rejection & -    & -      & -	  & 0.6\%        & 28.1\% & 3.5\%  \\
		\middlehline
		Channel 13  & Bias      & -0.00 &  -0.52 & -0.08 & -0.07 		& -0.14  & -0.29 \\
					& MAE       &  0.80 &   1.17 &  0.84 &  0.83  		&  0.86  &  0.97 \\
					& STD       &  1.00 &   3.04 &  1.13 &  1.10  		&  112  &	1.39 \\
					& skewness  &  0.02 & -17.85 & -1.14 & -0.98  		& -0.91  & -2.23 \\	
					& rejection   & -    & -      & -	  & 1.6\%        & 28.1\% & 3.5\%  \\	
		\middlehline
		Channel 15  & Bias      & -0.00 &  -1.28 & -0.07 & -0.06        & -0.33 &  -0.81 \\
					& MAE       &  0.80 &   1.87 &  0.97 &  0.92 		&  1.03 &	1.44 \\
					& STD       &  1.00 &   5.08 &  1.35 &  1.25 		&  1.53 &	2.64 \\
					& skewness  & -0.00 & -11.15 & -0.60 & -0.83 		& -2.85 &  -4.41 \\ 
					& rejection & -     & -      & -	 & 5.6\%        & 28.1\% & 3.5\%  \\
		\bottomhline
	\end{tabular}
\end{table*}
